%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 14: External Organizations/Clubs Use of RITSEC Resources
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Article{External Organizations}

% SECTION A: Purpose
\Section{Purpose}

\begin{enumerate}
	\item Allowing and establishing a process for external organizations to use RITSEC resources for their own needs.
	\item Any agreement between RITSEC and the external club/organization with relation to this article does not mean that the external org is now a part of RITSEC in any way. 
\end{enumerate}


% SECTION B: Process
\Section{Process}

\begin{enumerate}
	\item The leadership of the external org must submit a written request to an E-Board member at least 2 weeks before the requested time. This request must include the following:
	\begin{enumerate}
		\item The timeframe the resources are being requested for
		\item The reason for the request
		\item What resources are being requested
		\item Contact information
		\item Any other additional information
	\end{enumerate}
	\item The E-Board member must present this request to the E-Board at the next E-Board meeting no matter what. 
	\begin{enumerate} 
		\item If the E-Board member cannot attend the meeting, the responsibility passes on to the President (and follows the order of succession). 
	\end{enumerate}
	\item Any questions will be directed towards the contact information and must be performed before the following E-Board meeting. 
	\item Once everything else has been performed, a vote by all active E-Board members must reach a majority. 
	\begin{enumerate}
		\item Once this vote has passed or failed, the external org must be notified and either the request be fulfilled or the reason for the deny be given.
	\end{enumerate}
\end{enumerate}