%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 13: INDEPENDENT PROGRAMS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Independent Programs}

% SECTION A: LEADERSHIP
\subsection{Leadership}

\begin{enumerate}
  \item Program leads shall forever and henceforth be referred to as "chief" of
    their respective Independent programs.
  \item Chief appointment is up to the discretion of the Independent Program.
\end{enumerate}

% SECTION B: Creation
\subsection{Creation}

\begin{enumerate}
  \item All new Independent Programs must be added as amendments to the
    constitution (as shown in subsequent Sections).
  \item Have a purpose and goal for how the program will positively affect the
    club and it’s members.
\end{enumerate}

% SECTION C: FUNDING
\subsection{Funding}

\begin{enumerate}
  \item Funding for programs is approved by E-Board after petition from the
    chief.
\end{enumerate}

% SECTION D: INTEREST GROUP PROGRAM
\subsection{Interest Group Program}

% SUBSECTION 1: PURPOSE
\subsubsection{Purpose}

\begin{enumerate}
  \item Provide value to the club and its members.
  \item Provide a focused environment to study a specific field or topic.
\end{enumerate}

% SUBSECTION 2: SPECIAL PRIVILEGES
\subsubsection{Special Privileges}

\begin{enumerate}
  \item All approved Interest Groups have the ability to stream their events on
    the official RITSEC social media platforms under the following conditions.
  \begin{enumerate}
    \item A liability form is completed by the leader of the interest group for
      the streaming equipment.
    \item Only the individual who signed the liability is allowed to take out
      the equipment.
    \item A checkout form is filled out each time the equipment is added and
      removed from the club HQ.
    \item RITSEC events and meetings come first. Interest groups may not use
      the streaming equipment on the day of the official club weekly meeting or
      during official events such as keynote presentations and closing remarks.
    \item Swipe to HQ shall not be abused or violated.
    \item Failure to meet these conditions will result in revocation of
      streaming and swipe access and may result in disciplinary E-Board action.
  \end{enumerate}
  \item Funding
  \begin{enumerate}
    \item Each Interest Group is allocated \$100 of discretionary spending.
    \item Additional funding is available, given E-Board approval, through a
      simple majority of all EBoard members. 
  \end{enumerate}
\end{enumerate}

% SUBSECTION 3: LEADERSHIP
\subsubsection{Leadership}

\begin{enumerate}
  \item The Interest Group Program Chief is the E-Board secretary.
  \item Leadership of Interest Group Program is conducted by the Interest Group
    Program Chief.
  \item Leadership of each individual Interest Group is conducted by that
    Interest Group's leader.
\end{enumerate}

% SUBSECTION 4: REQUIREMENTS
\subsubsection{Requirements}

\begin{enumerate}
  \item Have an Interest Group leader.
  \item Have at least 3 members.
  \item The Interest Group must be approved by a vote including the E-Board.
\end{enumerate}

% SECTION E: MENTORSHIP PROGRAM
\subsection{Mentorship Program}

% SUBSECTION 1: PURPOSE
\subsubsection{Purpose}

\begin{enumerate}
  \item To enable more accessible learning through a small group setting.
  \item To promote security and involvement to underclassmen and incoming
    students.
  \item To build lasting relationships between students.
\end{enumerate}

% SUBSECTION 2: REQUIREMENTS FOR BEING A MENTOR
\subsubsection{Requirements for Being a Mentor}

\begin{enumerate}
  \item Must be an RITSEC member.
  \item Must be approved by the Mentorship Program Chief.
\end{enumerate}

% SECTION F: REDTEAM PROGRAM
\subsection{Redteam Program}

% SUBSECTION 1: PURPOSE
\subsubsection{Purpose}

\begin{enumerate}
  \item To teach members through adversary emulation.
  \item To provide a service to competitions run by RITSEC and other schools as
    needed.
\end{enumerate}

\subsubsection{Requirements}

\begin{enumerate}
  \item To qualify for Redteam, you must be a current or previous club member
  \item You must be approved by the Redteam Chief.
\end{enumerate}