%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 15: WiCyS at RIT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Article{WiCyS at RIT}

% SECTION A: Name
\Section{Name}

\begin{enumerate}
	\item Women in Cybersecurity (WiCyS) RIT Student Chapter
\end{enumerate}

% SECTION B: Purpose
\Section{Purpose}

\begin{enumerate}
	\item To keep alumnae connected to the RIT community and to strengthen the bond between current female students.
      \item Present opportunities through the WiCyS Organization, such as attending the annual conference and career fairs. 
      \item To ensure members are prepared and have the accessibility to land their dream jobs. 
\end{enumerate}


% SECTION C: WiCyS Non-Profit Organization
\Section{WiCyS Non-Profit Organization}

\begin{enumerate}
	\item WiCyS Non-Profit Organization
	      \begin{enumerate}
		      \item Local RIT chapter members do not need to be a member of the WiCyS International organization. Becoming a member is \$20 a year and allows access to the WiCyS Job Portal, Job Chat Portal, and the ability to be considered for a student scholarship to the annual WiCyS conference.
            \end{enumerate}
\end{enumerate}

% SECTION D: Target Audience
\Section{Target Audience}

\begin{enumerate}
	\item Women in CyberSecurity (WiCyS) is the premier organization with national reach dedicated to bringing together non-male identifying people in cybersecurity from academia, research and industry to share knowledge, experience, networking and mentoring. Membership in the WiCyS Student Chapter shall be open to all students within RIT without restrictions according to race, creed, age, gender, disability, nationality, sexual orientation, economic status, veteran status, or parenthood.
\end{enumerate}

% SECTION E: WiCyS Structure
\Section{WiCyS Structure}

\begin{enumerate}
      \item Liaison for RITSEC Eboard Meetings: The President of WiCyS shall serve as the official liaison for all meetings between WiCyS and RITSEC. The WiCyS President will represent the organization's interests, share updates, and facilitate communication between the two clubs. If the President cannot attend or is on the RITSEC E-Board then the line of succession will be followed and the next WiCyS E-Board member will attend as a non-voting member.
      \item Liaison for WiCyS Eboard Meetings: The Vice President of RITSEC shall serve as the official liaison for all meetings between WiCyS and RITSEC. The RITSEC Vice President will represent the organization's interests, share updates, and facilitate communication between the two clubs. If the Vice President cannot attend or is on the WiCyS E-Board then the line of succession will be followed and the next RITSEC E-Board member will attend as a non-voting member.
      \item Budget from RITSEC: WiCyS will receive a budget from RITSEC, contingent upon the availability of funds in the RITSEC budget. This budget will contribute to the successful execution of WiCyS events and initiatives.
      \item WiCyS Finances: WiCyS Treasurer will maintain open communication with the RITSEC treasurer on all major purchases that the club may need to make.
      \item Sponsorship: WiCyS will maintain open communication with RITSEC on all sponsorship opportunities.
\end{enumerate}