% SECTION D: INTEREST GROUP PROGRAM
\Section{Interest Group Program}

% SUBSECTION 1: PURPOSE
\Subsection{Purpose}

\begin{enumerate}
  \item Provide value to the club and its members.
  \item Provide a focused environment to study a specific field or topic.
\end{enumerate}

% SUBSECTION 2: SPECIAL PRIVILEGES
\Subsection{Special Privileges}

\begin{enumerate}
  \item All approved Interest Groups have the ability to stream their events on
    the official RITSEC social media platforms under the following conditions.
  \begin{enumerate}
    \item A liability form is completed by the leader of the interest group for
      the streaming equipment.
    \item Only the individual who signed the liability is allowed to take out
      the equipment.
    \item A checkout form is filled out each time the equipment is added and
      removed from the club HQ.
    \item RITSEC events and meetings come first. Interest groups may not use
      the streaming equipment on the day of the official club weekly meeting or
      during official events such as keynote presentations and closing remarks.
    \item Swipe to HQ shall not be abused or violated.
    \item Failure to meet these conditions will result in revocation of
      streaming and swipe access and may result in disciplinary E-Board action.
  \end{enumerate}
  \item Funding
  \begin{enumerate}
    \item Each Interest Group is allocated \$100 of discretionary spending.
    \item Additional funding is available, given E-Board approval, through a
      simple majority of all EBoard members. 
  \end{enumerate}
\end{enumerate}

% SUBSECTION 3: LEADERSHIP
\Subsection{Leadership}

\begin{enumerate}
  \item The Interest Group Program Chief is the E-Board secretary.
  \item Leadership of Interest Group Program is conducted by the Interest Group
    Program Chief.
  \item Leadership of each individual Interest Group is conducted by that
    Interest Group's leader.
\end{enumerate}

% SUBSECTION 4: REQUIREMENTS
\Subsection{Requirements}

\begin{enumerate}
  \item Have an Interest Group leader.
  \item Have at least 3 members.
  \item The Interest Group must be approved by an E-Board vote.
\end{enumerate}
