% SECTION G: OPERATIONS PROGRAM
\Section{Operations Program}

\Subsection{Definitions}

\begin{enumerate}
    \item The use of the term "RITSEC Cloud" in this context collectively
        refers to any RITSEC-owned compute, storage, and networking resources.
    \item The use of the term "the Program" in this context refers to the
        Operations Program.
\end{enumerate}

\Subsection{Purpose}

\begin{enumerate}
    \item The intent of the Program is to make it possible to maintain a highly
        available cloud for RITSEC club operations and the RITSEC members.
    \item The organization and operation of the Program is intended to reduce
        dependencies on individual people for the successful operation of the
        RITSEC cloud.
\end{enumerate}

\Subsection{Membership Requirements}

\begin{enumerate}
    \item The individual who holds the role of RITSEC Operations Lead will also
        hold the position of Operations Chief.
    \item The Operations Chief selects the members of the Program, and is
        responsible for ensuring to the best of their ability that there are a
        sufficient number of members to fulfill the Program's purpose.
    \item Members of the Program must commit to contributing equally to the
        Program. However, it is understood and accepted that occasional
        conflicts will arise that cause a Program member to temporarily be
        unable to fulfill this commitment.
    \item The membership of a Program member may be revoked through one of the
        following methods.
    \begin{enumerate}
        \item The Operations Chief may revoke the membership of a Program
            member at any time, provided that the revocation will not seriously
            negatively impact the Program's ability to fulfill its purpose.
        \item The RITSEC E-Board may revoke the membership of a Program member
            at any time with a majority vote, provided that the revocation will
            not seriously negatively impact the Program's ability to fulfill
            its purpose.
    \end{enumerate}
\end{enumerate}

\Subsection{Program Responsibilities}

\begin{enumerate}
    \item The Program must maintain the functionality and uptime of the RITSEC
        Cloud for club operations and club member projects.
    \item The Program must provide user documentation for the RITSEC Cloud and
        support club member use of the Cloud.
    \item The Program must maintain sufficient operator documentation to enable
        all Program members to maintain all RITSEC Cloud systems.
    \item The Program must help new Program members learn how to operate the
        RITSEC Cloud.
    \item The Program must deliver a report at the end of the year detailing
        the Program's achievements and goals for the next year.
    \item The Program must prioritize club operations over club member projects
        in the maintenance and resource usage of the RITSEC Cloud.
\end{enumerate}