%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 4: CLUB MEMBERSHIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Article{Club Membership}

% SECTION A: MEMBERSHIP TERMS
\Section{Membership Terms}

\begin{enumerate}
	\item To be an RITSEC club member, an individual must fulfill all the following
	      requirements.
	      \begin{enumerate}
		      \item Be actively enrolled part-time or full-time in an RIT undergraduate, graduate,
		            or doctoral degree program.
		            \begin{enumerate}
			            \item Students who are suspended from RIT will be ineligible for membership status
			                  during the suspension period.
		            \end{enumerate}
		      \item Meet at least one of the following requirements within a semester:
		            \begin{enumerate}
			            \item Attend at least three RITSEC club meetings.
			            \item Attend at least one RITSEC club meeting IF AND ONLY IF there has been no more
			                  than three RITSEC club meetings that semester.
			            \item Present during a meeting.
			            \item Member of an Independent Program as defined in 13 RITSEC.
		            \end{enumerate}
	      \end{enumerate}
	\item If an individual fulfills the requirements of membership as defined in 4 RITSEC
	      A(I), then they will be considered a member for the entire semester in which
	      they fulfilled the requirements.
	      % TODO: update citation
	\item At the end of a semester, an individual's current membership status will remain
	      unchanged until the beginning of the following semester unless the current
	      E-Board revokes their status as in 9 RITSEC D.
	      % TODO: update citation
	\item At the beginning of a new semester, an individual who maintained a membership
	      during the previous semester will have a provisional membership for the new
	      semester. If that individual does not fulfill the requirements as defined in 4
	      RITSEC A(I) during that semester of provisional membership, then their
	      provisional membership will be voided, and they will lose membership status for
	      that semester.
	      % TODO: update citation
	\item If a member takes a planned break from classes for a co-op, internship,
	      research position, other work position, or study abroad term, that does not
	      make them ineligible for membership as defined under 4 RITSEC A(I)(A); the
	      membership requirement defined under 4 RITSEC A(I)(B) shall be waived for that
	      member during that period of time.
	      % TODO: update citation
\end{enumerate}

% SECTION B: MEMBERSHIP REPORTING
\Section{Membership Reporting}

\begin{enumerate}
	\item E-Board is responsible for maintaining an accurate and up-to-date roster of
	      club members.
	      \begin{enumerate}
		      \item The roster of club members may be viewed only by other club members.
		      \item The roster of club members must include records of when an individual's
		            membership started, ended, and when applicable, temporarily lapsed.
	      \end{enumerate}
	\item If a company, nonprofit organization, government, or other legitimate
	      organization inquires about an individual's membership status, E-Board will
	      provide said organization with the individual's current membership status and
	      their membership history as recorded in the club roster.
	      \begin{enumerate}
		      \item E-Board will be required to provide an individual with their membership history
		            as recorded in the club roster if that individual is no longer a club member.
	      \end{enumerate}
\end{enumerate}