%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 7: A-BOARD STRUCTURE, RESPONSIBILITIES, AND ROLES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Article{A-Board Structure, Responsibilities, and Roles}

\Section{A-Board Status}
\begin{enumerate}
      \item A-Board members are considered club members, and possess all member rights.     
      \item Each individual on an A-Board position must directly report to those described
            in their respective sections.
      \item The creation of an A-Board position is at the discretion of the E-Board.
            \begin{enumerate}
                  \item Within two semesters of a new A-Board position being created, the position must
                        be added to 7 RITSEC as a new section.
                  \item In the event the position is not added to 7 RITSEC and the timeline expires,
                        the position will be discarded.
            \end{enumerate}
      \item A-Board Positions last from their appointment in the fall semester until the of the E-Board transition in the Spring Semester unless specified otherwise in the position itself. There will be no A-Board positions fulfilled during the summer time. All responsibilities of the A-Board Positions during the summertime are fulfilled or delegated by the E-Board position the A-Board position reports to.

\end{enumerate}

% SECTION A: WEB ADMIN
\Section{Web Admin}

\begin{enumerate}
      \item The interview process for this position is up to the discretion of the incoming
            E-Board.
      \item This position is appointed by a vote of the incoming E-Board.
      \item This position directly reports to the Vice President.
      \item Responsible for maintaining all RITSEC websites.
\end{enumerate}

% SECTION B: JUNIOR TECH LEAD
\Section{Junior Tech Lead}

\begin{enumerate}
      \item The interview process for this position is up to the discretion of the current
            Tech Lead.
      \item This position is appointed by a vote of the incoming E-Board.
      \item This position directly reports to and is responsible for assisting the current
            Tech Lead.
      \item This individual is unable to participate in the demos or obtain demo prizes.
\end{enumerate}

% SECTION C: HEAD OF SOCIAL MEDIA
\Section{Head of Social Media}

\begin{enumerate}
      \item The interview process for this position is up to the discretion of the current
            Head of Public Relations.
      \item This position is appointed by a vote of the incoming E-Board.
      \item This position directly reports to the Head of Public Relations.
      \item Responsible for maintaining all RITSEC Social Media.
\end{enumerate}
