%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 6: E-BOARD STRUCTURE, RESPONSIBILITIES, AND ROLES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Article{E-Board Structure, Responsibilities, and Roles}

% SECTION A: E-BOARD MEMBERS
\Section{E-Board Members}

\begin{enumerate}
  \item E-Board members are considered club members, and they can participate in all
    voting.
  \item Under no circumstances can E-Board win prizes from an RITSEC
    competition or RITSEC event run by E-Board.
  \item E-Board members have the right to RITSEC resources and funds with
    permission from the Treasurer or a vote by E-Board.
  \item E-Board members are responsible for attending and participating in all
    E-Board meetings.
  \item The list below states the chain of succession of the RITSEC E-Board.
    The chain of succession is as follows:
  \begin{enumerate}
    \item President
    \item Vice President
    \item Secretary
    \item Treasurer
    \item ISTS Competition Architect 
    \item IRSeC and CTF Competition Architect
    \item Director of Public Relations
    \item Tech Lead
    \item Operations Lead
    \item Head of Research or Head of Education 
    \begin{enumerate}
      \item Succession will be decided by a coin toss
    \end{enumerate}
  \end{enumerate}
\end{enumerate}

% SECTION B: PRESIDENT
\Section{President}

\begin{enumerate}
  \item This position is elected by the club members.
  \item This position is the face of club and E-Board.
  \item Preside over and exercise general supervision over RITSEC events. 
  \item Preside over the E-Board.
  \item Attend or send an alternate member to all auxiliary meetings involving the club.
  \item Maintain the RITSEC E-Board calendar.
\end{enumerate}

% SECTION C: VICE PRESIDENT
\Section{Vice President}

\begin{enumerate}
  \item This position is elected by the club members.
  \item Retained by the President as a supporting role.
  \item Assist in RITSEC endeavors as decided by E-Board.
  \item Preside over the A-Board.
  \item In charge of all newly created A-Board positions unless, otherwise assigned.
\end{enumerate}

% SECTION D: SECRETARY
\Section{Secretary}

\begin{enumerate}
  \item This position is elected by the club members.
  \item Responsible for communication between E-Board and club members:
  \begin{enumerate}
    \item Recording and publishing E-Board's weekly meeting notes publicly to the club body.
    \item Managing the livestream and recordings of club meetings and all other qualifying meetings. 
    \item Maintaining RITSEC's public calendar.
  \end{enumerate}
  \item Responsible for communicating with Interest Groups and Programs and their respective chiefs.
  \item Responsible for handling transition of power for Interest Groups.
\end{enumerate}

% SECTION E: TREASURER
\Section{Treasurer}

\begin{enumerate}
  \item This position is elected by the club members.
  \item Responsible for all financial transactions of all aspects of the organization and keep all financial records up to date. This includes, but is not limited to:
  \begin{enumerate} 
    \item Crafting a budget encompassing all entities contained under the RITSEC namespace.
    \item Maintaining a ledger for each and all entities under the RITSEC namespace.
  \end{enumerate}
\end{enumerate}

% SECTION F: ISTS CA
\Section{ISTS Competition Architect} 

\begin{enumerate}
  \item This position is elected by the club members.
  \item Design and oversee the ISTS competition.
  \item Preside over their respective Black Team.
\end{enumerate}

% SECTION G: IRSeC / RITSEC CTF CA
\Section{IRSeC / RITSEC CTF Competition Architect} 

\begin{enumerate}
  \item This position is elected by the club members.
  \item Design and oversee the IRSeC and CTF competitions.
  \item Preside over their respective Black Team. 
\end{enumerate}

% SECTION H: DIRECTOR OF PUBLIC RELATIONS
\Section{Director of Public Relations}

\begin{enumerate}
  \item This position is elected by the club members.
  \item Act as the publicly facing individual for RITSEC pertaining to organizations outside RIT. % TODO Olivia is assuming this is the main diff btwn PR and Pres? 
  \item Responsible for all interactions with sponsors and/or potential sponsors.
  \item Responsible for approving any RITSEC-branded merchandise.
  \item Organize and preside over the selection process for the Head of Social Media. 
\end{enumerate}

% SECTION I: TECH LEAD
\Section{Tech Lead}

\begin{enumerate}
  \item This position is appointed by a vote of the departing E-Board.
  \item Responsible for designing and distributing technical demos of weekly meetings.
  \item Organize and preside over the selection process for the Junior Tech Lead. 
\end{enumerate}

% SECTION J: OPERATIONS LEAD
\Section{Operations Lead}

\begin{enumerate}
  \item This position is appointed by a vote of the departing E-Board.
  \item Responsible for the Operations Program.
  \item Assumes the role of Operations Chief.
\end{enumerate}

% SECTION K: HEAD OF EDUCATION
\Section{Head of Education}

\begin{enumerate}
  \item This position is elected by the club members.
  \item Supervise club activities within the education portion of a club meeting.
  \item Ensure a presentation has been created for the security topic of the week.
  \item Assist the Tech Lead with weekly demos.
\end{enumerate}

% SECTION L: HEAD OF RESEARCH
\Section{Head of Research}

\begin{enumerate}
  \item This position is elected by the club members.
  \item Supervise club activities within the research portion of a club meeting.
  \item Shall actively seek out and promote research opportunities to be undertaken by RITSEC.
  \item Review all research grant request forms submitted by members. 
  \item Manage weekly news at the research meetings.
\end{enumerate}
