%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 10: AMENDMENTS TO THE CONSTITUTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Article{Amendments to the Constitution}

% SECTION A: REVIEW
\Section{Review}

\begin{enumerate}
  \item The constitutional by-laws contained herein shall come under review
    with the expectation of modernization, at most, every five years since the
    last major edit. This review is the responsibility of the President and the Vice President.
  \item All amendments must be recorded at the bottom of this constitution with
    the date and the E-Board members who officially changed it.
\end{enumerate}

% SECTION B: E-BOARD CONSTITUTION AMENDMENTS
\Section{E-Board Constitution Amendments}

\begin{enumerate}
  \item E-Board has the right to veto any amendment proposed by a club member
    to the constitution. 10 RITSEC C(IV) defines how club members can circumvent 
    an E-Board veto.
    % TODO: update citation
  \item E-Board also has the right to make amendments to the constitution
    and/or bylaws. A vote by all active E-Board members must reach at least
    three-fourths majority to make amendments to the constitution and/or
    bylaws. Once the vote has passed E-Board must present the change(s) to the
    club.
  \begin{enumerate}
    \item E-Board must expressly identify the changes made in the amendment as
      well as show the original. E-Board must provide publicly available copies
      of the Constitution.
  \end{enumerate}
  \item If club members disapprove of the new amendments to the
    constitution and/or bylaws, they may override it. This override will follow
    the procedures detailed in 10 RITSEC C(IV).
    % TODO: update citation
\end{enumerate}

% SECTION C: CLUB MEMBER AMENDMENTS
\Section{Club Member Constitution Amendments}

\begin{enumerate}
  \item In the event a club member wishes to change the constitution and/or
    bylaws, they must first notify E-Board. The club member must then submit, at
    minimum, a summary of the changes they wish to make, to the RITSEC E-Board. 
    These changes must be identified as detailed in 10 RITSEC ยง B(II)(A).
    % TODO: update citation
  \item E-Board must make time to discuss the change(s) at the nearest E-Board
    meeting or, at most, two weeks after the documents are received. The
    E-Board must decide to veto or approve the proposed changes.
  \item If approved, the club member must then present their petitioned change
    to the entire club. The club members will then vote on the petitioned
    change and must reach three-fourths majority to pass.
  \item The members may override E-Board's decision or veto by reaching a
    three-fourths majority in a club vote.
\end{enumerate}

\Section{Amendments to the Constitution}
  \subsection{6 September 2021}
  \begin{enumerate}
    \item Clarifications to Member Rights and A-Board Positions.

      \subsubsection{Articles/Bylaws Modified}
      \begin{enumerate}
        \item Article 3, Section II
        \item Article 7, Sections I, II, III
        \item Article 10, Section IV
      \end{enumerate} 

      \subsubsection{Proposing Individual}
      \begin{enumerate}
        \item Enzo DeStephano
      \end{enumerate}
  \end{enumerate}
  \subsection{18 March 2022}
    \begin{enumerate}
      \item Reorganization and Clarification of E-Board Roles and Responsibilities. 
      \item Addition of Vice President position to E-Board. 
      \item Separation of Competition Architect into ISTS Competition Architect and IRSeC / CTF Architect.
      \item Definition and addition of the Head of Social Media.
      \item Addition of RITSEC Competition Terms in Terms section.
      \item Overall Grammar and Organizational Fixes.
  
        \subsection{Articles/Bylaws Modified}
        \begin{enumerate}
          \item Terms
          \item Article 1
          \item Article 2
          \item Article 3
          \item Article 4, Section I
          \item Article 5, Section II
          \item Article 6, Sections I, II, III, IV, V, VI, VIII, IX, X, XI
          \item Article 7, Sections I, II, IV
          \item Article 9, Sections I, IV, VI
          \item Article 10, Sections I, IV
          \item Article 12
          \item Article 13, Sections I, IV
        \end{enumerate} 
  
        \subsection{Date Modified}
        \begin{enumerate}
          \item 21 February 2022
        \end{enumerate}
  
        \subsection{Proposing Individual}
        \begin{enumerate}
          \item Maxwell Fusco
          \item Enzo DeStephano
          \item Jason Howe
          \item Olivia Gallucci
        \end{enumerate}
    \end{enumerate}
    
