%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 5: RULES AND REGULATIONS FOR ELECTIONS AND VOTING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Article{Rules and Regulations for Elections and Voting}

% SECTION A: METHODS FOR ELECTIONS
\Section{Methods for Elections}

\begin{enumerate}
	\item The E-Board should give adequate and fair time and resources to each candidate
	      during the election process.
	\item Each candidate's platform must be made available to the voting members prior to
	      a vote.
	\item Adequate time must be allocated for discussion of the candidates for a position
	      among the club members not running for that position.
	\item E-Board has the responsibility to run a fair and just Ranked Choice Voting
	      election.
\end{enumerate}

% SECTION B: METHODS OF CLUB MEMBER VOTING
\Section{Methods of Club Member Voting}

\begin{enumerate}
	\item In order for a vote to be counted, the member must be present at the RITSEC
	      Event where the vote is being held.
	      \begin{enumerate}
		      \item If an RITSEC member is unable to be physically present at the vote because of a
		            break as defined in 4 RITSEC A (V), they may submit an absentee ballot in a
		            process dictated by E-Board.
	      \end{enumerate}
	\item No member shall vote in the place of another member, forge a vote, or attempt
	      to double count a vote.
\end{enumerate}

% SECTION C: METHODS OF VOTING FOR EXECUTIVE BOARD DECISIONS
\Section{Methods of Voting for Executive Board Decisions}

\begin{enumerate}
	\item Issues that require an E-Board vote must involve all members of the E-Board,
	      even if they cannot all vote at the same time or through the same method.
	      \begin{enumerate}
		      \item An E-Board member may choose to vote in favor of an issue, vote against an
		            issue, or abstain from an issue. However, all E-Board members must explicitly
		            choose one of those three options for each issue.
	      \end{enumerate}
	\item After a vote, the tallies of each vote should be recorded.
	      \begin{enumerate}
		      \item This record should never be released to the club members.
	      \end{enumerate}
\end{enumerate}