%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 9: RITSEC CODE OF CONDUCT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Article{RITSEC Code of Conduct}

% SECTION A: CLUB MEMBER CODE OF CONDUCT
\Section{Club Member Code of Conduct}

\begin{enumerate}
  \item All RITSEC members are expected to promote the core values of RITSEC
  \begin{enumerate}
    \item Club Members - Our top priority is our club members. Without our club
      members, there is no RITSEC.
    \item Respect - Gaining and building mutual respect from each other and our
      industry peers is critical to the success of our club.
    \item Ethics - It is important as a club and as individuals that we strive
      "to do the right thing".
    \item Empowerment - Critical to the success of any organization is to
      create an environment and culture whereby club members are empowered to
      make a positive impact.
    \item Dedication - As club members and as individuals, we strive to be
      dedicated to our pursuit for knowledge, to our Core Values, and to each
      other.
  \end{enumerate}
  \item All RITSEC members are expected to treat each other with respect,
    including their opinions and points of view.
  \item All RITSEC members are expected to help create a safe and engaging
    environment for all members.
  \item All RITSEC members are expected to promote the rules of the RITSEC Code
    of Conduct and take action whenever inappropriate behaviors are observed.
  \item All RITSEC members are expected to report hazing and harassment. Hazing
    and harassment are against RITSEC’s Code of Conduct.
\end{enumerate}

% SECTION B: E-BOARD CONDUCT ARBITRATION
\Section{E-Board Conduct Arbitration}

\begin{enumerate}
  \item E-Board is responsible for taking action to resolve club conflict and
    to address Code of Conduct breaches.
  \item This action may include suspension or revocation of club membership as
    detailed in 9 RITSEC D.
    % TODO: update citation
\end{enumerate}

% SECTION C: RIT'S STUDENT CONDUCT DEPARTMENT
\Section{RIT's Student Conduct Department}

\begin{enumerate}
  \item In the event an RITSEC arbitration does not correct the member’s
    behavior, RITSEC E-Board may report the member’s behavior to RIT’s Student
    Conduct Department. 
  \begin{enumerate}
    \item RITSEC E-Board retains the the right to bypass the process of
      arbitration if the behavior is serious enough to warrant the attention of
      RIT’s Student Conduct Department.
    \item RITSEC E-Board retains the right to include or withhold the member in
      talks and any information given or received from RIT’s Student Conduct
      Department.
  \end{enumerate}
\end{enumerate}

% SECTION D: REVOKING CLUB MEMBERSHIP
\Section{Revoking Club Membership}

\begin{enumerate}
  \item RITSEC E-Board retains the right to revoke any member’s club membership
    status for not adhering to the Code of Conduct in the RITSEC Constitution
    and Bylaws. 
  \begin{enumerate}
    \item Revoking club membership may include, but is not limited to removing
      their points from weekly challenges and removing the association of the
      member from social media pertaining to RITSEC.
    \item Revoking club membership can be permanent or for a specified amount
      of time, and is at the discretion of RITSEC E-Board.
  \end{enumerate}
  \item RITSEC E-Board retains the right to inform Public Safety and the
    Computing Security department if a member who has lost their membership
    status or is not welcome at RITSEC events.
  \item In the event of revocation of membership the ex-member be banned or
    denied from any RITSEC Events.
\end{enumerate}

% SECTION E: RITSEC EVENTS
\Section{RITSEC Events}

\begin{enumerate}
  \item All RITSEC events may have rules on how attendees must conduct
    themselves. RITSEC E-Board retains the right to create additional rules
    during the event if the need arises. If a member or participant decides to
    not follow the competitions rules, the E-Board may take the following
    actions. 
  \begin{enumerate}
    \item Altering the state of the event to penalize the attendee.
    \item Banning an attendee(s) or team from an RITSEC event.
  \end{enumerate}
\end{enumerate}

% SECTION F: DESTRUCTION OF RITSEC PROPERTY
\Section{Destruction of RITSEC Property}

\begin{enumerate}
  \item All members and guests (e.g. visiting schools) of RITSEC are expected
    to treat all RITSEC property with respect and care. If a member or guests
    damages or destroys RITSEC property, they are required to repair it and pay
    for any damages. If the student is unable to afford repairs, RITSEC E-Board
    will contact RIT’s Student Conduct Department pertaining to the situation.
\end{enumerate}