%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 8: IMPEACHMENT, STEPPING DOWN, OR ABSENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO: rename to "Impeachment, Stepping Down, and Absences
% TODO: what happened to the absences section?

\section{Impeachment, Stepping Down, or Absence}

% SECTION A: IMPEACHMENT
\section{Impeachment}

\begin{enumerate}
  \item All active E-Board members, including the subject of the impeachment
    proceedings must be present when starting the hearings for impeachment.
  \item The subject of the impeachment hearings will be given the time to
    explain their situation to their peers.
  \begin{enumerate}
    \item In the event the subject of the impeachment is unwilling to attend
      these meetings or does not provide an adequate time for their hearing,
      E-Board may proceed without the individual in attendance.
  \end{enumerate}
  \item At the end of the hearing, the subject of the impeachment proceedings
    will be asked to leave the room so deliberation can take place. After the
    discussion, a vote will be taken of all hearing attendees. At least
    three-fourths of the hearing attendees must vote to impeach the subject for
    the impeachment to be sustained.
    % TODO: replace "hearing attendees" with "the hearing's attendees" so we
    % don't look like we're discriminating against the deaf/HoH
  \item If the subject of impeachment is the President the Chain of Succession
    will be followed in the member’s absence.
  \item E-Board may choose to appoint a new candidate or delegate the tasks
    that were held by the subject of impeachment.
  \begin{enumerate}
    \item If the subject is an E-Board member, the rest of the E-Board shall
      hold an election for that position before the next academic semester as
      detailed in 5 RITSEC § A.
      % TODO: update citation
  \end{enumerate}
  \item Any 2 members may propose an impeachment.
  \begin{enumerate}
    \item E-Board must accept or veto the proposal of impeachment.
    \item The club can overrule E-Board's decision given a three-fourths
      majority to impeach the subject of impeachment.
  \end{enumerate}
\end{enumerate}

% SECTION B: STEPPING DOWN
\subsection{Stepping Down}

\begin{enumerate}
  \item Any person in a subject of responsibility may step down and is hereto
    referred as the subject.
  \item In the event a subject of responsibility must step down from their
    position, they must give a two-week notice to the entire E-Board.
    % TODO: the subject is defined in the previous paragraph but not used here
  \begin{enumerate}
    \item If the subject is the President the Chain of Succession will be
      followed in the member’s absence.
  \end{enumerate}
  \item E-Board may choose to appoint a new candidate or delegate the tasks
    that were held by the member who stepped down.
  \begin{enumerate}
    \item If the subject is an E-Board member, the rest of the E-Board shall
      hold an election for that position before the next academic semester as
      detailed in 5 RITSEC § A.
      % TODO: update citation
  \end{enumerate}
\end{enumerate}