\documentclass{article}

\usepackage[margin=1in]{geometry}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TERMS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\part{Terms}

\begin{itemize}
  \item Executive Board (E-Board) - RITSEC’s primary leadership structure.
    Members of E-Board hold the trust of the club members to make decisions for
    the club's benefit and longevity. E-Board Members will be appointed
    according to the defined election proceedings.
  \item Assistance Board (A-Board) - The assistance board will provide support
    to E-Board for competitions, events, and goals. Members of A-Board will
    report to E-Board members. A-Board Members will be appointed according to
    the defined election proceedings.
  \item Impeachment - The forced removal of an E-Board, A-Board, Club Advisor
    member from their position within RITSEC.
    % TODO: remove advisor reference
  \item Absence - An absence is an E-Board, A-Board, Club Advisor member who
    has a responsibility to attend an RITSEC meeting, RITSEC E-Board meeting,
    RITSEC event, or RITSEC competition and does not. Reasons for absence are
    defined in Article 7 Subsection C: Absences.
    % TODO: update citation
  \item Stepping down - An RITSEC E-Board, A-Board, Club Advisor that chooses
    to give up their position and responsibilities.
    % TODO: remove advisor reference
  \item Club Member - A club member is recognized by RITSEC as an individual
    who has fulfilled the requirements for club membership as defined in
    Article 4.
    % TODO: update citation
  \item RITSEC Event - An event using RITSEC resources and/or RITSEC funds or
    that is ran or promoted by RITSEC.
  \item RITSEC Competition - An event which is security-related and competitive
    in nature and separate from regular RITSEC meetings.
  \item Independent Programs - A program that provides benefit to RITSEC and
    its members for which it receives funding, and has independent governance.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CONSTITUTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\part{Constitution}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 1: NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Name}

\begin{enumerate}
  \item The name of this club/organization is RITSEC. For the rest of this
    document the club/organization will be referred to as RITSEC. RITSEC is not
    short for “RIT Security”. RITSEC is not an acronym.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 2: PURPOSE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Purpose}

\begin{enumerate}
  \item RITSEC is a student run organization that prepares students to be
    competitive in the growing field of computing security. RITSEC prepares
    students by organizing and hosting competitions, hosting weekly meetings,
    and enabling independent student research. RITSEC centers around live
    individual and team-based security exercises covering a wide variety of
    areas in computing security.
  \item While the club has activity in many different areas including but not
    limited to: other schools, organizations, sponsors, alumni groups, and RIT
    faculty, the club functions first and foremost for the students at
    Rochester Institute of Technology and decisions shall be made with their
    best interests in mind.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 3: RIGHTS AND RESPONSIBILITIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Rights and Responsibilities}

\begin{enumerate}
  \item E-Board has the responsibility to provide a club meeting on a weekly
    basis; this must include a time dedicated to education and a time dedicated
    to research
  \begin{enumerate}
    \item E-Board has the right to not hold or to cancel a meeting on any given
      week when it is deemed beneficial to the club not to hold the meeting for
      that week. Or due to unsafe or unpredicted circumstances.
      % TODO: combine sentences into one sentence
  \end{enumerate}
  \item Active club members have several privileges associated with their
    membership status.
  \begin{enumerate}
    \item Shall have the right to run for Executive Board positions
    \item Shall become alumni members upon graduation
    \item Shall be confirmed a member if asked by a company
    \item Shall have the right to request funding for projects and/or research
  \end{enumerate}
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 4: CLUB MEMBERSHIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Club Membership}

% SECTION A: MEMBERSHIP TERMS
\subsection{Membership Terms}

\begin{enumerate}
  \item To be an RITSEC club member, an individual must fulfill all the
    following requirements.
  \begin{enumerate}
    \item Be actively enrolled part-time or full-time in an RIT undergraduate,
      graduate, or doctoral degree program.
    \begin{enumerate}
      \item Students who are suspended from RIT will not be eligible for
        membership status during the period of their suspension.
    \end{enumerate}
  \end{enumerate}
  \begin{enumerate}
    \item Meet at least one of the following requirements within a semester.
    \begin{enumerate}
      \item Attend at least three RITSEC club meetings.
      \item Attend at least one RITSEC club meeting IF AND ONLY IF there has
        been no more than three RITSEC club meetings that semester.
      \item Present during a meeting.
      \item Participate in an Independent Program as defined in 14 RITSEC.
    \end{enumerate}
  \end{enumerate}
  \item If an individual fulfills the requirements of membership as defined in
    4 RITSEC § A(I), then they will be considered a member for the entire
    semester in which they fulfilled the requirements.
    % TODO: update citation
  \item At the end of a semester, an individual's current membership status
    will remain unchanged until the beginning of the following semester unless
    the current EBoard revokes their status as in 13 RITSEC § C.
    % TODO: update citation
  \item At the beginning of a new semester, an individual who maintained a
    membership during the previous semester will have a provisional membership
    for the new semester. If that individual does not fulfill the requirements
    as defined in 4 RITSEC § A(I) during that semester of provisional
    membership, then their provisional membership will be voided and they will
    lose membership status for that semester.
    % TODO: update citation
  \item If a member takes a planned break from classes for a co-op, internship,
    research position, other work position, or study abroad term that does not
    make them ineligible for membership as defined under 4 RITSEC § A(I)(A),
    then the membership requirement defined under 4 RITSEC § A(I)(B) shall be
    waived for that member during that period of time.
    % TODO: update citation
\end{enumerate}

% SECTION B: MEMBERSHIP REPORTING
\subsection{Membership Reporting}

\begin{enumerate}
  \item E-Board is responsible for maintaining an accurate and up-to-date
    roster of club members.
  \begin{enumerate}
    \item The roster of club members may be viewed only by other club members.
    \item The roster of club members must include records of when an
      individual's membership started, ended, and when applicable, temporarily
      lapsed.
  \end{enumerate}
  \item If a company, nonprofit organization, government, or other legitimate
    organization inquires about an individual's membership status, E-Board will
    provide said organization with the individual's current membership status
    and their membership history as recorded in the club roster.
  \begin{enumerate}
    \item E-Board will be required to provide an individual with their
      membership history as recorded in the club roster if that individual is
      no longer a club member.
  \end{enumerate}
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 5: RULES AND REGULATIONS FOR ELECTIONS AND VOTING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Rules and Regulations for Elections and Voting}

% SECTION A: METHODS FOR ELECTIONS
\subsection{Methods for Elections}

\begin{enumerate}
  \item The E-Board should give adequate and fair time and resources to each
    candidate during the election process.
  \item Each candidate's platform must be made available to the voting members
    prior to a vote.
  \item Adequate time must be allocated for discussion of the candidates for a
    position among the club members not running for that position.
  \item E-Board has the responsibility to run a fair and just Ranked Choice
    Voting election.
\end{enumerate}

% SECTION B: METHODS OF CLUB MEMBER VOTING
\subsection{Methods of Club Member Voting}

\begin{enumerate}
  \item In order for a vote to be counted the member must be present at the
    RITSEC Event where the vote is being held.
  \item No member shall vote in the place of another member or in any way forge
    their vote or attempt to double count their vote.
\end{enumerate}

% SECTION C: METHODS OF VOTING FOR EXECUTIVE BOARD DECISIONS
\subsection{Methods of Voting for Executive Board Decisions}

\begin{enumerate}
  \item Issues that require an E-Board vote must involve all members of the
    E-Board, even if they cannot all vote at the same time or through the same
    method.
  \begin{enumerate}
    \item An E-Board member may choose to vote in favor of an issue, vote
      against an issue, or abstain from an issue.  However, all E-Board members
      must explicitly choose one of those three options for each issue.
  \end{enumerate}
  \item After a vote, the tallies of each vote should be recorded.
  \begin{enumerate}
    \item This record should never be released to the club members.
  \end{enumerate}
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 7: E-BOARD STRUCTURE, RESPONSIBILITIES, AND ROLES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{E-Board Structure, Responsibilities, and Roles}

% SECTION A: E-BOARD MEMBERS
\subsection{E-Board Members}

\begin{enumerate}
  \item E-Board members are considered club members, and can participate in all
    voting.
  \item Under no circumstances can E-Board win prizes from an RITSEC
    competition or RITSEC event run by E-Board.
  \item E-Board members have the right to RITSEC resources and funds with
    permission from the Treasurer or a vote by E-Board.
  \item E-Board members are responsible for attending and participating in all
    E-Board meetings.
  \item The list below states the chain of succession of the RITSEC E-Board.
    The chain of succession is as follows:
  \begin{enumerate}
    \item President
    \item Secretary
    \item Treasurer
    \item Competition Architect 
    \item Director of Public Relations
    \item Tech Lead
    \item Operations Lead
    \item Head of Research or Head of Education as decided by a coin toss
  \end{enumerate}
\end{enumerate}

% SECTION B: PRESIDENT
\subsection{President}

\begin{enumerate}
  \item This position is elected by the club members.
  \item Preside over and exercise general supervision over RITSEC events. 
  \item Preside over the Executive Board.
  \item Attend or send an alternate member to all auxiliary meetings involving
    the club.
  \item Maintain the RITSEC E-Board calendar.
  \item Attend weekly RITSEC meetings
\end{enumerate}

% SECTION C: HEAD OF EDUCATION
\subsection{Head of Education}

\begin{enumerate}
  \item This position is elected by the club members.
  \item Share the role of supervising all club activities within the education
    sector of the club.
  \item Ensure a presentation has been created for the security topic of the
    week.
  \item Assist the Teach Lead in weekly demos.
  \item Attend weekly RITSEC meetings.
\end{enumerate}

% SECTION D: HEAD OF RESEARCH
\subsection{Head of Research}

\begin{enumerate}
  \item This position is elected by the club members.
  \item Shall actively seek out and promote research opportunities to be
    undertaken by RITSEC.
  \item Review all research grant request forms submitted by members. 
  \item Manage weekly news at the research meetings.
  \item Promote and encourage students to engage in research.
  \item Attend weekly RITSEC meetings.
\end{enumerate}

% SECTION E: COMPETITION ARCHITECT
\subsection{Competition Architect}

\begin{enumerate}
  \item This position is elected by the club members.
  \item Design and oversee all RITSEC competitions.
\end{enumerate}

% SECTION F: DIRECTOR OF PUBLIC RELATIONS
\subsection{Director of Public Relations}

\begin{enumerate}
  \item This position is elected by the club members.
  \item Act as the publicly facing individual for RITSEC pertaining to
    organizations outside RIT.
  \item Responsible for all interactions with sponsors potential sponsors.
  \begin{enumerate}
    \item At all times the Director of Public Relations must treat these
      entities with respect.
  \end{enumerate}
  \item Responsible for approving any RITSEC branded merchandise.
\end{enumerate}

% SECTION G: TREASURER
\subsection{Treasurer}

\begin{enumerate}
  \item This position is elected by the club members.
  \item Responsible for all financial transactions of all aspects of the organization and keep all financial records up to date.
  \begin{enumerate}
    \item Maintain a ledger for each club entity.
    \item Maintain a budget for each Independent Program.
  \end{enumerate}
\end{enumerate}

% SECTION H: SECRETARY
\subsection{Secretary}

\begin{enumerate}
  \item This position is elected by the club members.
  \item Responsible for communication between E-Board and club members.
  \begin{enumerate}
    \item Responsible for recording and publishing meeting notes to the club
      body.
    \item Responsible for managing the stream and recordings of weekly meetings
      and all other qualifying meetings.
  \end{enumerate}
  \item Responsible for communicating with Independent Program chiefs.
  \item Assumes the role of Interest Group Chief.
\end{enumerate}

% SECTION G: OPERATIONS LEAD
\subsection{Operations Lead}

\begin{enumerate}
  \item This position is appointed by a vote of the departing E-Board.
  \item Responsible for maintaining the infrastructure and technical services
    of RITSEC.
\end{enumerate}

% SECTION H: TECH LEAD
\subsection{Tech Lead}

\begin{enumerate}
  \item This position is appointed by a vote of the departing E-Board.
  \item Responsible for the technical aspect of weekly meetings.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 8: A-BOARD STRUCTURE, RESPONSIBILITIES, AND ROLES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{A-Board Structure, Responsibilities, and Roles}

% SECTION A: WEB ADMIN
\subsection{Web Admin}

\begin{enumerate}
  \item This position is appointed by a vote of the incoming E-Board. 
  \item Responsible for maintaining all RITSEC websites.
\end{enumerate}

% SECTION B: JUNIOR COMPETITION ARCHITECT
\subsection{Junior Competition Architect}

\begin{enumerate}
  \item This position is appointed by a vote of the incoming E-Board.
  \item Responsible for assisting Competition Architect.
\end{enumerate}

% SECTION C: JUNIOR TECH LEAD
\subsection{Junior Tech Lead}

\begin{enumerate}
  \item This position is appointed by a vote of the incoming E-Board.
  \item Responsible for assisting the Tech Lead.
\end{enumerate}

% SECTION D: JUNIOR OPERATIONS LEAD
\subsection{Junior Operations Lead}

\begin{enumerate}
  \item This position is appointed by a vote of the incoming E-Board.
  \item Responsible for assisting the Operations Lead.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 9: IMPEACHMENT, STEPPING DOWN, OR ABSENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO: rename to "Impeachment, Stepping Down, and Absences
% TODO: what happened to the absences section?

\section{Impeachment, Stepping Down, or Absence}

% SECTION A: IMPEACHMENT
\section{Impeachment}

\begin{enumerate}
  \item All active E-Board members, including the subject of the impeachment
    proceedings must be present when starting the hearings for impeachment.
  \item The subject of the impeachment hearings will be given the time to
    explain their situation to their peers.
  \begin{enumerate}
    \item In the event the subject of the impeachment is unwilling to attend
      these meetings or does not provide an adequate time for their hearing,
      E-Board may proceed without the individual in attendance.
  \end{enumerate}
  \item At the end of the hearing, the subject of the impeachment proceedings
    will be asked to leave the room so deliberation can take place. After the
    discussion, a vote will be taken of all hearing attendees. At least
    three-fourths of the hearing attendees must vote to impeach the subject for
    the impeachment to be sustained.
    % TODO: replace "hearing attendees" with "the hearing's attendees" so we
    % don't look like we're discriminating against the deaf/HoH
  \item If the subject of impeachment is the President the Chain of Succession
    will be followed in the member’s absence.
  \item E-Board may choose to appoint a new candidate or delegate the tasks
    that were held by the subject of impeachment.
  \begin{enumerate}
    \item If the subject is an E-Board member, the rest of the E-Board shall
      hold an election for that position before the next academic semester as
      detailed in 5 RITSEC § A.
      % TODO: update citation
  \end{enumerate}
  \item Any 2 members may propose an impeachment.
  \begin{enumerate}
    \item E-Board must accept or veto the proposal of impeachment.
    \item The club can overrule E-Board's decision given a three-fourths
      majority to impeach the subject of impeachment.
  \end{enumerate}
\end{enumerate}

% SECTION B: STEPPING DOWN
\subsection{Stepping Down}

\begin{enumerate}
  \item Any person in a subject of responsibility may step down and is hereto
    referred as the subject.
  \item In the event a subject of responsibility must step down from their
    position, they must give a two-week notice to the entire E-Board.
    % TODO: the subject is defined in the previous paragraph but not used here
  \begin{enumerate}
    \item If the subject is the President the Chain of Succession will be
      followed in the member’s absence.
  \end{enumerate}
  \item E-Board may choose to appoint a new candidate or delegate the tasks
    that were held by the member who stepped down.
  \begin{enumerate}
    \item If the subject is an E-Board member, the rest of the E-Board shall
      hold an election for that position before the next academic semester as
      detailed in 5 RITSEC § A.
      % TODO: update citation
  \end{enumerate}
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 10: RITSEC CODE OF CONDUCT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{RITSEC Code of Conduct}

% SECTION A: CLUB MEMBER CODE OF CONDUCT
\subsection{Club Member Code of Conduct}

\begin{enumerate}
  \item All RITSEC members are expected to promote the core values of RITSEC
  \begin{enumerate}
    \item Club Members - Our top priority is our club members. Without our club
      members, there is no RITSEC.
    \item Respect - Gaining and building mutual respect from each other and our
      industry peers is critical to the success of our club.
    \item Ethics - It is important as a club and as individuals that we strive
      "to do the right thing".
    \item Empowerment - Critical to the success of any organization is to
      create an environment and culture whereby club members are empowered to
      make a positive impact.
    \item Dedication - As club members and as individuals, we strive to be
      dedicated to our pursuit for knowledge, to our Core Values, and to each
      other.
  \end{enumerate}
  \item All RITSEC members are expected to treat each other with respect,
    including their opinions and points of view.
  \item All RITSEC members are expected to help create a safe and engaging
    environment for all members.
  \item All RITSEC members are expected to promote the rules of the RITSEC Code
    of Conduct and take action whenever inappropriate behaviors are observed.
  \item All RITSEC members are expected to report hazing and harassment. Hazing
    and harassment are against RITSEC’s Code of Conduct.
\end{enumerate}

% SECTION B: E-BOARD CONDUCT ARBITRATION
\subsection{E-Board Conduct Arbitration}

\begin{enumerate}
  \item E-Board is responsible for taking action to resolve club conflict and
    to address Code of Conduct breaches.
  \item This action may include suspension or revocation of club membership as
    detailed in 10 RITSEC § D.
    % TODO: update citation
\end{enumerate}

% SECTION C: RIT'S STUDENT CONDUCT DEPARTMENT
\subsection{RIT's Student Conduct Department}

\begin{enumerate}
  \item In the event an RITSEC arbitration does not correct the member’s
    behavior, RITSEC E-Board may report the member’s behavior to RIT’s Student
    Conduct Department. 
  \begin{enumerate}
    \item RITSEC E-Board retains the the right to bypass the process of
      arbitration if the behavior is serious enough to warrant the attention of
      RIT’s Student Conduct Department.
    \item RITSEC E-Board retains the right to include or withhold the member in
      talks and any information given or received from RIT’s Student Conduct
      Department.
  \end{enumerate}
\end{enumerate}

% SECTION D: REVOKING CLUB MEMBERSHIP
\subsection{Revoking Club Membership}

\begin{enumerate}
  \item RITSEC E-Board retains the right to revoke any member’s club membership
    status for not adhering to the Code of Conduct in the RITSEC Constitution
    and Bylaws. 
  \begin{enumerate}
    \item Revoking club membership may include, but is not limited to removing
      their points from weekly challenges and removing the association of the
      member from social media pertaining to RITSEC.
    \item Revoking club membership can be permanent or for a specified amount
      of time, and is at the discretion of RITSEC E-Board.
  \end{enumerate}
  \item RITSEC E-Board retains the right to inform Public Safety and the
    Computing Security department if a member who has lost their membership
    status or is not welcome at RITSEC events.
  \item In the event of revocation of membership the ex-member be banned or
    denied from any RITSEC Events.
\end{enumerate}

% SECTION E: RITSEC EVENTS
\subsection{RITSEC Events}

\begin{enumerate}
  \item All RITSEC events may have rules on how attendees must conduct
    themselves. RITSEC E-Board retains the right to create additional rules
    during the event if the need arises. If a member or participant decides to
    not follow the competitions rules, the E-Board may take the following
    actions. 
  \begin{enumerate}
    \item Altering the state of the event to penalize the attendee.
    \item Banning an attendee(s) or team from an RITSEC event.
  \end{enumerate}
\end{enumerate}

% SECTION F: DESTRUCTION OF RITSEC PROPERTY
\subsection{Destruction of RITSEC Property}

\begin{enumerate}
  \item All members and guests (e.g. visiting schools) of RITSEC are expected
    to treat all RITSEC property with respect and care. If a member or guests
    damages or destroys RITSEC property, they are required to repair it and pay
    for any damages. If the student is unable to afford repairs, RITSEC E-Board
    will contact RIT’s Student Conduct Department pertaining to the situation.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 11: AMENDMENTS TO THE CONSTITUTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Amendments to the Constitution}

% SECTION A: REVIEW
\subsection{Review}

\begin{enumerate}
  \item The constitutional by-laws contained herein shall come under review
    with the expectation of modernization, at most, every five years since the
    last major edit. This review is the responsibility of the president and the
    secretary.
  \item All amendments must be recorded at the bottom of this constitution with
    the date and the E-Board members who officially changed it.
\end{enumerate}

% SECTION B: E-BOARD CONSTITUTION AMENDMENTS
\subsection{E-Board Constitution Amendments}

\begin{enumerate}
  \item E-Board has the right to veto any amendment proposed by a club member
    to the constitution. 11 RITSEC § C defines how club members can circumvent
    an E-Board veto.
    % TODO: update citation
  \item E-Board also has the right to make amendments to the constitution
    and/or bylaws. A vote by all active E-Board members must reach at least
    three-fourths majority to make amendments to the constitution and/or
    bylaws. Once the vote has passed E-Board must present the change(s) to the
    club.
  \begin{enumerate}
    \item E-Board must expressly identify the changes made in the amendment as
      well as show the original. E-Board must provide publicly available copies
      of the Constitution.
  \end{enumerate}
  \item If club members do not approve of the new amendments to the
    constitution and/or bylaws, they may override it. This override will follow
    the procedures detailed in 11 RITSEC § C(IV).
    % TODO: update citation
\end{enumerate}

% SECTION C: CLUB MEMBER AMENDMENTS
\subsection{Club Member Constitution Amendments}

\begin{enumerate}
  \item In the event a club member wishes to change the constitution and/or
    bylaws they must first notify E-Board. The club member must then submit, at
    minimum, a summary of the changes they wish to make to the RITSEC E-Board.
    These changes must be identified as detailed in 11 RITSEC § B(II)(A).
    % TODO: update citation
  \item E-Board must make time to discuss the change(s) at the nearest E-Board
    meeting or, at most, two weeks after the documents are received. The
    E-Board must decide to veto or approve the proposed changes.
  \item If approved, the club member must then present their petitioned change
    to the entire club. The club members will then vote on the petitioned
    change and must reach three-fourths majority to pass.
  \item The members may override E-Board's decision or veto by reaching a
    three-fourths majority in a club vote.
\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BYLAWS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\part{Bylaws}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 12: TRANSITION OF POWER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Transition of Power}

\begin{enumerate}
  \item Any E-Board or A-Board member who steps down, graduates, or is
    impeached from their position must follow the “RITSEC Transition of Powers”
    document. This document discloses the access for each position and the
    access that must be revoked for that member. 
    % TODO: document doesn't exist
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 13: SUSPENSION OF THE BYLAWS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Suspension of the Bylaws}

\begin{enumerate}
  \item Any club member can motion to suspend the bylaws within the RITSEC
    Constitution with approval from RITSEC E-Board. A written motion must be
    submitted to RITSEC E-Board for consideration, and must include the
    rationale for why the bylaw should be suspended and a time frame for which
    the suspension shall be in effect. The RITSEC E-Board needs at least
    three-fourths E-Board vote to approve the suspension.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARTICLE 14: INDEPENDENT PROGRAMS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Independent Programs}

% SECTION A: LEADERSHIP
\subsection{Leadership}

\begin{enumerate}
  \item Program leads shall forever and henceforth be referred to as "chief" of
    their respective Independent programs.
  \item Chief appointment is up to the discretion of the Independent Program.
\end{enumerate}

% SECTION B: Creation
\subsection{Creation}

\begin{enumerate}
  \item All new Independent Programs must be added as amendments to the
    constitution (as shown in subsequent Sections).
  \item Have a purpose and goal for how the program will positively affect the
    club and it’s members.
\end{enumerate}

% SECTION C: FUNDING
\subsection{Funding}

\begin{enumerate}
  \item Funding for programs is approved by E-Board after petition from the
    chief.
\end{enumerate}

% SECTION D: INTEREST GROUP PROGRAM
\subsection{Interest Group Program}

% SUBSECTION 1: PURPOSE
\subsubsection{Purpose}

\begin{enumerate}
  \item Provide value to the club and its members.
  \item Provide a focused environment to study a specific field or topic.
\end{enumerate}

% SUBSECTION 2: SPECIAL PRIVILEGES
\subsubsection{Special Privileges}

\begin{enumerate}
  \item All approved Interest Groups have the ability to stream their events on
    the official RITSEC social media platforms under the following conditions.
  \begin{enumerate}
    \item A liability form is completed by the leader of the interest group for
      the streaming equipment.
    \item Only the individual who signed the liability is allowed to take out
      the equipment.
    \item A checkout form is filled out each time the equipment is added and
      removed from the club HQ.
    \item RITSEC events and meetings come first. Interest groups may not use
      the streaming equipment on the day of the official club weekly meeting or
      during official events such as keynote presentations and closing remarks.
    \item Swipe to HQ shall not be abused or violated.
    \item Failure to meet these conditions will result in revocation of
      streaming and swipe access and may result in disciplinary E-Board action.
  \end{enumerate}
  \item Funding
  \begin{enumerate}
    \item Each Interest Group is allocated \$100 of discretionary spending.
    \item Additional funding is available, given E-Board approval, through a
      simple majority of all EBoard members. 
  \end{enumerate}
\end{enumerate}

% SUBSECTION 3: LEADERSHIP
\subsubsection{Leadership}

\begin{enumerate}
  \item The Interest Group Program Chief is the E-Board secretary.
  \item Leadership of Interest Group Program is conducted by the Interest Group
    Program Chief.
  \item Leadership of each individual Interest Group is conducted by that
    Interest Group's leader.
\end{enumerate}

% SUBSECTION 4: REQUIREMENTS
\subsubsection{Requirements}

\begin{enumerate}
  \item Have an Interest Group leader.
  \item Have at least 3 members.
  \item The Interest Group must be approved by a vote including the E-Board.
\end{enumerate}

% SECTION E: MENTORSHIP PROGRAM
\subsection{Mentorship Program}

% SUBSECTION 1: PURPOSE
\subsubsection{Purpose}

\begin{enumerate}
  \item To enable more accessible learning through a small group setting.
  \item To promote security and involvement to underclassmen and incoming
    students.
  \item To build lasting relationships between students.
\end{enumerate}

% SUBSECTION 2: REQUIREMENTS FOR BEING A MENTOR
\subsubsection{Requirements for Being a Mentor}

\begin{enumerate}
  \item Must be an RITSEC member.
  \item Must be approved by the Mentorship Program Chief.
\end{enumerate}

% SECTION F: REDTEAM PROGRAM
\subsection{Redteam Program}

% SUBSECTION 1: PURPOSE
\subsubsection{Purpose}

\begin{enumerate}
  \item To teach members through adversary emulation.
  \item To provide a service to competitions run by RITSEC and other schools as
    needed.
\end{enumerate}

\subsubsection{Requirements}

\begin{enumerate}
  \item To qualify for Redteam, you must be a current or previous club member
  \item You must be approved by the Redteam Chief.
\end{enumerate}

\end{document}
