\begin{itemize}
      \item Executive Board (E-Board) - RITSEC's primary leadership structure. Members of
            E-Board hold the trust of the club members to make decisions for the club's
            benefit and longevity. E-Board Members will be appointed according to the
            defined election proceedings.

      \item Assistance Board (A-Board) - The A-Board will provide support to E-Board for
            competitions, events, and goals. Members of A-Board will report to assigned
            E-Board members. A-Board Members will be appointed according to the defined
            election proceedings.

      \item Impeachment - The forced removal of an E-Board or A-Board member from their
            position within RITSEC.

      \item Absence - An absence is an E-Board, A-Board, Club Advisor, or member who has a
            responsibility to attend an RITSEC meeting, RITSEC E-Board meeting, RITSEC
            event, or RITSEC competition and does not.

      \item Stepping down - An RITSEC E-Board or A-Board member that chooses to give up
            their position and responsibilities.

      \item Club Member - A club member is recognized by RITSEC as an individual who has
            fulfilled the requirements for club membership as defined in 4 RITSEC A(I).

      \item RITSEC Event - An event using RITSEC resources and/or RITSEC funds or that is
            ran or promoted by RITSEC.

      \item RITSEC Competition - An event which is security-related and competitive in
            nature and separate from regular RITSEC meetings.

      \item Independent Programs - A program that provides benefit to RITSEC and its
            members for which it receives funding and has independent governance.

      \item Information Security Talent Search (ISTS) - A subset of RITSEC Competitions.
            ISTS is a several day collegiate Advanced Blue/Red Competition with features
            such as Purple Teaming, King of the Hill, and other elements.

      \item Incident Response Security Competition (IRSeC) - A subset of RITSEC
            Competitions. IRSeC is a single day Blue/Red beginner competition open to only
            students at RIT.

      \item RITSEC CTF - A subset of RITSEC Competitions which is a several day
            Jeopardy-style Capture the Flag Competition that is open to anyone.

      \item Black Team - A subset of RITSEC Competitions which is a group of individuals
            chosen by Competition Architects which are responsible for the development and
            production of their respective events.

\end{itemize}