% SECTION D: RED TEAM
\Section{RITSEC Red Team}

% SUBSECTION 1: NAME
\Subsection{Name}

\begin{enumerate}
	\item RITSEC Red Team
\end{enumerate}

% SUBSECTION 2: PURPOSE
\Subsection{Purpose}

\begin{enumerate}
	\item To perform the role of an effective adversary to blue teams at RITSEC and
	      affiliated competitions
	\item To grow the skills and knowledge in red teaming, software development, and
	      offensive security within RITSEC.\@
\end{enumerate}

% SUBSECTION 3: TARGET AUDIENCE
\Subsection{Target Audience}

\begin{enumerate}
	\item Those interested in learning more about red teaming, operating system
	      (in)security, offensive security tactics, techniques, and procedures (TTPs),
	      tool development, infrastructure, and supporting RITSEC competitions.
\end{enumerate}

% SUBSECTION 4: REQUIREMENTS
\Subsection{Requirements}

\begin{enumerate}
	\item There are no requirements to join the RITSEC Red Team.
	\item To gain deployment rights, allowing a member to deploy tools to competition
	      infrastructure, one must:
	      \begin{enumerate}
		      \item Compete in two RITSEC or affiliated competitions on a blue team. Outside blue
		            team experience can be optionally considered by the RITSEC Red Team Chief. This
		            requirement is to introduce the team member to competition blue teaming, the
		            ``competition spirit'', and to gain familiarity with incident response.
		      \item Design and implement at least one red team tool or overhaul an existing RITSEC
		            Red Team tool. This includes the tool itself, appropriate testing (to ensure
		            functionality and stability), documentation (to help other team members use the
		            tool), and deployment (to deploy the tool before competitions in an automated
		            fashion). The stability must be ensured before this requirement is met, and is
		            subject to the RITSEC Red Team Chief's approval. This requirement is to
		            introduce tool development to the team member, synthesizing an idea into a
		            practical capability. Previously written tools may apply.
		      \item Demonstrate fairness and good sportsmanship. RIT Redteam often competes against
		            teams from several different schools as well as against their friends and
		            peers. It is very important to maintain fairness and impartiality in these
		            situations.
		      \item Be a team player. RITSEC Red Team is a group effort. If you are not willing to
		            be a team player and be respectful to your peers (Blue, Red, and White team),
		            then we have no interest in the talents that you might bring to the table. We
		            work closely with all the different teams in order to effectively be part of
		            the competition.
		      \item You must have a 1-on-1 Meeting with the RITSEC Red Team Chief. At the end of
		            your time in Recruiting, you will have a conversation with the Red Team Chief.
		            This is a business casual conversation, where you will get to know the RITSEC
		            Red Team Chief. You'll discuss what you learned about the RITSEC Red Team, what
		            your personal goals are, and what Competition Spirit means to you.
	      \end{enumerate}
	\item Deployment rights is defined as competing as a part of the RITSEC Red Team in
	      competitions
\end{enumerate}