% SECTION K: OPERATIONS PROGRAM
\Section{Operations Program}

% SUBSECTION 1: NAME
\Subsection{Name}

\begin{enumerate}
	\item Operations Program
\end{enumerate}

% SUBSECTION 2: PURPOSE
\Subsection{Purpose}

\begin{enumerate}
	\item To perform the role of maintaining the RITSEC physical and Cloud infrastructure
	      with high availability and security standards.
\end{enumerate}

% SUBSECTION 3: TARGET AUDIENCE
\Subsection{Target Audience}

\begin{enumerate}
	\item Those interested in learning more about DevSecOps, operating systems, system
	      administration, networking, cloud computing, and software development, where
	      security is considered.
\end{enumerate}

% SUBSECTION 4: REQUIREMENTS
\Subsection{Requirements}

\begin{enumerate}
	\item The individual who holds the role of RITSEC Operations Lead will also hold the
	      position of Operations Chief.
	\item The Operations Chief selects the Operations Program members and is responsible
	      for ensuring to the best of their ability that there are a sufficient number of
	      members to fulfill the Operations Program's purpose.
	\item Operations Program members must attend all operations meetings to the best of
	      their ability to discuss their progress and plans. They must commit to
	      contributing equally to the Program.
	\item The membership of an Operations Program member may be revoked through one of
	      the following methods:
	      \begin{enumerate}
		      \item The Operations Chief may revoke the membership of a Program member at any time,
		            provided that the revocation will not negatively impact the Program's ability
		            to fulfill its purpose.
		      \item The RITSEC E-Board may revoke the membership of a Program member at any time
		            with a majority vote, provided that the revocation will not seriously
		            negatively impact the Program's ability to fulfill its purpose.
	      \end{enumerate}
\end{enumerate}